Pillar 1 - Student Topic Profile

### 2019-04-16 Pillar 1 - Topic Profile.Rmd

Topic chosen by model are related to the course.
```{r}
i <- 2; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # topic ~ law, foreign policy, culture
i <- 12; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # history of western pol. thought predicted by HUM
i <- 3; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # topic ~ literature, art, culture
```

@@

View(fit_lasso_topic)
```

@@

View(d_prep)
```

>>>>

Topic chosen by model are related to the course.
```{r}
beta <- topic_model_gb$b_overview[[15]] %>% group_by(topic) %>% top_n(15, beta)

i <- 2; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Contemporary Classical Sociology: topic ~ law, foreign policy, culture
beta %>% filter(topic == "Topic 18")
beta %>% filter(topic == "Topic 8" )

i <- 12; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Business Administration: topic ~ business
beta %>% filter(topic == "Topic 19")

i <- 3; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # Culture, Politics and SOciety in Contemporary Asia: topic ~ law, international, policy
beta %>% filter(topic == "Topic 21") 
beta %>% filter(topic == "Topic 23")

i <- 9; fit_lasso$coefi[[i]]; fit_lasso$target[[i]] # history of Western Political Thought: GPA_HUM and topic ~ natural science
beta %>% filter(topic == "Topic 7") 
```

@@

print(fit_lasso_topic)
```

@@

print(d_prep)
```
